State of the Practice for Lattice Boltzmann Method Software

### 2022-10-09 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/ResubmissionResponseToReviewer.tex

\begin{document}

\begin{letter}{~\\
    ~\\
    ~\\
    ~\\
    Dr.\ Eugenio O\~{n}ate\\
    Editor-in-Chief\\
    Archives of Computational Methods in Engineering\\
    ~\\
    {\bf Re: Revisions to ARCO-D-22-00308R1, State of the Practice for Lattice
    Boltzmann Method Software}}

  \opening {Dear Dr.\ O\~{n}ate:}

  Thank you and the reviewer for the feedback on our submission.  The reviewer
  provided thoughtful and constructive comments.  In response to your e-mail,
  dated August 26, 2022, we have revised the paper to incorporate the requested
  revisions.  We provide a summary below.  The revised submission also includes
  a ``diff'' version of the paper showing the additions and deletions.

  While addressing the reviewer's comments, we noticed a minor inconsistency in
  several of our figures.  In the original submission we inadvertently used the
  AHP scores from our 10\% sensitivity analysis, rather than using the collected
  data directly. Correcting this in the resubmission does not alter any of our
  conclusions, but it does change the appearance of the figures for the AHP
  scores (Figures 3--12). Some summary tables also had to be modified, since
  with less artificial noise in the data there are more ties in the scores and
  some minor shifting in the rankings.  The ``diff'' version of the paper shows
  the minor changes in the discussion that arose from correcting the pairwise
  comparison data.  In the diff versions of Tables 7 and 11 show many additions
  and deletions, but this is because the difference tool bases its calculations
  on the syntax.  Although there are more ties in the corrected scores and some
  minor shifts in position, the general trends in the rankings are unchanged.

@@

  \textbf{Reviewer \#1}

  \begin{enumerate}
  \item The anonymization of the authors poses some challenges in evaluating
  the paper because the citations for the methodology and the raw data
  underlying the study have been anonymized away. \medskip

    \emph{We have removed the anonymization in the resubmission.  \smallskip}

  \item I think it would be useful to have slightly more by way of explanation
  here --- to provide a bit more understanding of the process followed for
  readers who choose not to pursue the details provided in the reference.  Two
  key steps to put a little more flesh around would be (1) how are the entries
  of the measurement template (Fig 2) turned into a single numerical score for
  the section, and (2) how is the aggregate AHP score obtained?  As to the first
  point, for example, I look at the Installability Overall Impression scores,
  which I initially took to be a numerical score for installability, but in the
  AHP Installability scores shown in Fig 3, there is no correlation between the
  number in the measurement template and the final score. \medskip

    \emph{In addition to removing the anonymization that hid some details, we have expanded Section 2.6 where we explain how we used Saaty's Analytic Hierarchy Process (AHP).  Specifically, we explain AHP's central idea of pairwise comparison, the process for performing an AHP ranking, and how we map from our subjective scores to Saaty's scores.  We also include, in Table 3, sample calculations. We also added text to Section 3.11 (Overall Quality), to explain how we use the priority ranking of qualities to combine the separate quality rankings into an overall ranking.\smallskip}

  \item In Fig 2, I see responses for ``Descriptive error messages?'' of yes, no,
  and n/a.  I have a hard time imagining what n/a could mean in this context.
  Presumably the installer either provides descriptive error messages or it does
  not?  Is this explained in one of the anonymized references or in the raw
  dataset, which I can't access either due to anonymization. \medskip

    \emph{The source of the confusion here is a space-saving edit to the question we used for collecting data.  The original question for grading the software was: ``If install fails were there descriptive error messages?'' To make the text fit in the limited space for the paper, we changed this to ``Descriptive error messages?''.   In retrospect, we can see how this is confusing.  The case of n/a applies when there were no errors in the installation, but the short-form version removed this key information.  The revised Figure 2 text removes the confusion by restoring the original text: ``If install fails were there descriptive error messages?''\smallskip}

@@

  \item AHP is left completely to outside references, and I think it would be
  beneficial to have at least a brief description here. \medskip

    \emph{Yes, we agree with the reviewer.  As mentioned above, Section 2.6 and 3.11 were expanded to give details on AHP. \smallskip}

  \item I think there was a statement that AHP weights all of the qualities
  equally, but in the graphs of the scores for various qualities (e.g., Figs
  3--6), there are dramatic differences in the ranges of the scores given to the
  packages --- anywhere from 0.06 as the top score to nearly 0.16.  The highest
  overall score is ~0.075 (Fig 12). So what is the *theoretical* top score in
  any category and overall?  Are there some categories in which even the
  highest-scoring packages are quite low on the absolute scale?  If so, I would
  think such situations deserve some discussion. \medskip

    \emph{The meaning of the AHP scores should be clearer now that we have
    explained the details of the method.  In our revisions we added the
    following sentence (in Section 2.6) to address the reviewer's concern: ``For
    the AHP method, the sum of the final $s_j$ values for a given quality is
    1.0.''  As a consequence of this, a low top score occurs when there is
    little to distinguish the packages from one another.  The reviewer is
    correct that we weigh each of the qualities equally, but that is only
    relevant when we are combining the quality rankings into an overall ranking,
    as described in Section 3.11. \smallskip}

### 2022-10-09 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Changes for the resubmitted version of the SOP of LBM

In our work, we make the common assumption of a reciprocal relationship between
options $k$ and $j$; that is, $A_{kj}=1/A_{jk}$.  A partial view of $A$ for the
quality of installability is found in Table~\ref{Tbl_SampleAHP}.  To obtain the
overall score for each option for a given criterion we use matrix $B$, where
$B_{jk} = A_{jk}/\sum_{i=1}^{i=n}(A_{i k})$.  That is, to get $B$ we normalize
the columns of $A$ by dividing by the sum of the entries in the column, as shown
in Table~\ref{Tbl_SampleAHP}.  For a given quality, the score ($s_j$) for
software package $j$ is found by averaging the entries in row $j$ of $B$.  That
is, $s_j = \frac{1}{n} \sum_{i=1}^{i=n}(B_{j i})$, as shown in the final column
of Table~\ref{Tbl_SampleAHP}. Sorting the $s_j$ values provides a ranking for
the software packages for the quality under investigation.  The $s_j$ values can
be combined for all qualities for an overall ranking, as discussed in
Section~\ref{Sec_OverallQuality}.

@@

Current LBM software mostly follows best practices, as illustrated by
Table~\ref{topperformerstable}, which summarizes the top two packages for each
quality and for the overall quality. Taking the union of all entries in the
table that appear under 2 or more qualities, we have 16 top performers:
ESPREsSo, MechSys, OpenLB, DL\_MESO (LBE), Sailfish, Ludwig, Musubi, pyLBM,
waLBerla, laboetie, lettuce, \esp, LUMA, Palabos, TCLB and LB2D-Prime.
Therefore, two thirds (67\%) of the 24 packages appear in the top two for at
least two qualities.  Almost all the top performers are alive, except for two
packages: laboetie and LB2D-Prime.  Alive packages are in a healthy state with
respect to adopting best practices.

>>>>

In our work, we make the common assumption of a reciprocal relationship between
options $k$ and $j$; that is, $A_{kj}=1/A_{jk}$.  A partial view of $A$ for the
quality of installability is found in Table~\ref{Tbl_SampleAHP}.  To obtain the
overall score for each option for a given criterion we use matrix $B$, where
$B_{jk} = A_{jk}/\sum_{i=1}^{i=n}(A_{i k})$.  That is, to get $B$ we normalize
the columns of $A$ by dividing by the sum of the entries in the column, as shown
in Table~\ref{Tbl_SampleAHP}.  For a given quality, the score ($s_j$) for
software package $j$ is found by averaging the entries in row $j$ of $B$.  That
is, $s_j = \frac{1}{n} \sum_{i=1}^{i=n}(B_{j i})$, as shown in the final column
of Table~\ref{Tbl_SampleAHP}. For the AHP method, the sum of the final $s_j$ values for a given quality is 1.0. Sorting the $s_j$ values provides a ranking for
the software packages for the quality under investigation.  The $s_j$ values can
be combined for all qualities for an overall ranking, as discussed in
Section~\ref{Sec_OverallQuality}.

@@

Current LBM software mostly follows best practices, as illustrated by
Table~\ref{topperformerstable}, which summarizes the packages ranked first and
second for each quality and for the overall quality. Taking the union of all
entries in the table that appear under 2 or more qualities, we have 16 top
performers: ESPREsSo, MechSys, OpenLB, DL\_MESO (LBE), Sailfish, Ludwig, Musubi,
pyLBM, waLBerla, laboetie, lettuce, \esp, LUMA, Palabos, TCLB and LB2D-Prime.
Therefore, two thirds (67\%) of the 24 packages appear in the top two for at
least two qualities.  Almost all the top performers are alive, except for two
packages: laboetie and LB2D-Prime.  Alive packages are in a healthy state with
respect to adopting best practices.
